---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/mdsumner/spex.svg?branch=master)](https://travis-ci.org/mdsumner/spex)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/spex?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/spex)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/spex)](https://cran.r-project.org/package=spex)
[![Coverage Status](https://img.shields.io/codecov/c/github/mdsumner/spex/master.svg)](https://codecov.io/github/mdsumner/spex?branch=master)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/spex)](http://cran.r-project.org/web/packages/spex/index.html)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## spex

Spatial extent with projection metadata. 

Create a fully-fledged SpatialPolygonsDataFrame *extent* from any object understood
by the 'raster' package function 'extent()'. If the input has projection metadata it
will be carried through to the output. 

There is also a method to put an extent and a crs together. 

## Installation

Install 'spex' from CRAN. 

```{r,eval=FALSE}
install.packages("spex")
```

## Examples

Create a Spatial object as a single extent polygon from a raster. 

```{r}
library(spex)
library(raster)
data(lux)
(exlux <- spex(lux))

## put an extent and a CRS together
spex(extent(0, 1, 0, 1), crs = "+proj=laea +ellps=WGS84")
```

Create a simple features POLYGON object from a raster. 

```{r}
library(spex)
library(raster)
r <- raster(volcano)
tm <- system.time(p <- qm_rasterToPolygons(r))

nrow(p)

head(p)

print(tm)
```
## TODO

* 'byid' for multi-objects
* by-group for multi objects
* raster edge extent with pixel corner vertices
* max segment length densification, in crs or by great-circle

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
